Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-13 programlogic.tex
+

\begin{figure*}
  \begin{lstlisting}[language=Coq]
 Definition $\vaddr\mapsto_{\textsf{t}}\{\textsf{q}\}\; \vpage$ : vProp $\Sigma$ := 
  $\exists_{\textsf{l4e l3e l2e l1}} \ldotp$  $\ulcorner$ aligned $\vaddr \urcorner \ast$ L4_L1_PointsTo(maddr l4e l3e l2e l1e) $\ast$ addr_L1$(\vaddr,\textsf{l1e}) \mapsto_{p} \vpage$.
 Definition L4_L1_PointsTo (rtv maddr l4e l3e l2e l1e :word 64) : vProp $\Sigma$ :=
  (l4M52 maddr rtv) \$\sim$\ (l4off maddr rtv) $\mapsto_{a}$ {q1}  l4e  $\ast$
  (l3M52 maddr l4e) \$\sim$\ (l3off maddr l4e)  $\mapsto_{a}$ {q2}  l3e $\ast$ 
  (l2M52 maddr l3e) \$\sim$\ (l2off maddr l3e) $\mapsto_{a}$ {q3}  l2e $\ast$
  (l1M52 maddr l2e) \$\sim$\ (l1off maddr l2e) $\mapsto_{a}$ {q4}  l1e.
\end{lstlisting}
\caption{A Strong Virtual Points-to Relation}
\todo[inline,color=red]{Colin says: shouldn't ther be a fraction q in the body of the virtual pointsto def?
I know this is just a sketch that we then move away from, but it's worth getting accurate.}
\todo[inline,color=cyan]{Colin says: the virtual points-to here is not defined as a vprop! the body is an iProp,
containing an unbound variable rtv, which should be the cr3val taken as an argument. (Also, rtv doesn't make sense to me
as a shorthand, why not cr3val?). I'm also pretty sure the maddr in the virtual points-to definition should be va.}
  \label{fig:strongvirtualpointsto}
\end{figure*}

@@

  \begin{figure*}
\[
\begin{array}{l}
  \mathcal{I}\textsf{ASpace}(\ptablestore,m)\stackrel{\triangle}{:=} \exists\;\gammaPred \ldotp \; \lambda\textsf{ rtv} \ldotp \; \ulcorner m \; !!\; \textsf{rtv} = \textsf{Some } \gammPred \urcorner \ast
    \ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}} \ast \\
  \bigast{(\vaddr, \textsf{l1e})\in \ptablestore}{\exists\;(\textsf{l4e l3e l2e})\ldotp \textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\textsf{ maddr, l4e, l3e, l2e, l1e})}
\end{array}
\]
\caption{Global Address-Space Invariant with a fixed global map of address-space names $m$}
  \label{fig:peraspaceinvariant}
  \end{figure*}

>>>>

\begin{figure*}
  \begin{lstlisting}[language=Coq]
 Definition $\vaddr\mapsto_{\textsf{t}}\{\textsf{q}\}\; \vpage$ : vProp $\Sigma$ := 
  $\exists_{\textsf{l4e l3e l2e l1}} \ldotp$  $\ulcorner$ aligned $\vaddr \urcorner \ast$ L4_L1_PointsTo(maddr l4e l3e l2e l1e) $\ast$ addr_L1$(\vaddr,\textsf{l1e}) \mapsto_{p} \vpage$.
 Definition L4_L1_PointsTo (maddr l4e l3e l2e l1e :word 64) : vProp $\Sigma$ :=
 $\lambda$ cr3val.
  (l4M52 maddr cr3val) \$\sim$\ (l4off maddr cr3val) $\mapsto_{a}$ {q1}  l4e  $\ast$
  (l3M52 maddr l4e) \$\sim$\ (l3off maddr l4e)  $\mapsto_{a}$ {q2}  l3e $\ast$ 
  (l2M52 maddr l3e) \$\sim$\ (l2off maddr l3e) $\mapsto_{a}$ {q3}  l2e $\ast$
  (l1M52 maddr l2e) \$\sim$\ (l1off maddr l2e) $\mapsto_{a}$ {q4}  l1e.
\end{lstlisting}
\caption{A Strong Virtual Points-to Relation}
\todo[inline,color=red]{Colin says: shouldn't ther be a fraction q in the body of the virtual pointsto def?
I know this is just a sketch that we then move away from, but it's worth getting accurate.}
\todo[inline,color=cyan]{Colin says: the virtual points-to here is not defined as a vprop! the body is an iProp,
containing an unbound variable rtv, which should be the cr3val taken as an argument. (Also, rtv doesn't make sense to me
as a shorthand, why not cr3val?). I'm also pretty sure the maddr in the virtual points-to definition should be va.}
  \label{fig:strongvirtualpointsto}
\end{figure*}

@@

  \begin{figure*}
\[
\begin{array}{l}
  \mathcal{I}\textsf{ASpace}(\ptablestore,m)\stackrel{\triangle}{=} \textsf{ASpace\_Lookup}(\ptablestore,m) \ast \\
 \qquad\qquad\qquad \bigast{(\vaddr, \textsf{l1e})\in \ptablestore}{\exists\;(\textsf{l4e l3e l2e})\ldotp \textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\textsf{ maddr, l4e, l3e, l2e, l1e})} \\
  \textsf{ where } \\
   \textsf{ASpace\_Lookup} (\ptablestore,m) \stackrel{\triangle}{=} \lambda\textsf{ cr3val} \ldotp \; \ulcorner m \; !!\; \textsf{cr3val} = \textsf{Some } \gammPred \urcorner \ast
    \ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}}

\end{array}
\]
\caption{Global Address-Space Invariant with a fixed global map of address-space names $m$}
  \label{fig:peraspaceinvariant}
  \end{figure*}
